Malacology: A Programmable Storage System Built on Ceph

### 2016-05-08 paper/paper.tex
full page package
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
modified:   paper.tex 	More changes to the intro

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Extending file system metadata by a new type of inode that together with Ceph's capability subsystem implements high-performance, non-durable access serialization
  \item
    Re-using Ceph's PAXOS-based consensus infrastructure for versioning of metadata service load-balancing policies
  \item
    Re-using storage objects for persisting policies
  \item
    Extending object interface classes for new logical storage/metadata devices
  \end{enumerate}
\item
  Two example implementations and evaluations for feasibility of services that use this framework

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called Zlog which is based on CORFU~\cite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service using Malacology~\cite{sevilla:sc15-mantle}
  \item 
    An application of the Mantle metadata load balancing service to manage 
  \end{enumerate}
\end{itemize}

>>>>

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Extending file system metadata by a new type of ``sequencer'' inode that together with Ceph's capability subsystem implements high-performance, non-durable access serialization
  \item
    Re-using Ceph's PAXOS-based consensus infrastructure for versioning of metadata service load-balancing policies
  \item
    Re-using storage objects for persisting policies
  \item
    Extending object interface classes for new logical storage/metadata devices
  \end{enumerate}
\item
  Two example implementations and evaluations for feasibility of services that use this framework

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called Zlog which is based on CORFU~\cite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service using Malacology~\cite{sevilla:sc15-mantle}
  \item 
    An application of the Mantle metadata load balancing service to manage the placement of new sequencer inodes.
  \end{enumerate}
\end{itemize}
